\section{Hardware Results and Discussions}

\subsection{Results}
The hardware project showed be reliable and robust. The project amplified
well the electric signal to be used by the firmware, digitizing the signal
perfectly. It has difficult on the project start with the delay to have
the pickup base. The project showed be challenging, assemble completely a
hexaphonic pickup and the amplifier system, but it was successfully performed.

\subsection{Future Improvements}
For the future and thinking on production it is thought to test some INA 326 IC
for other supplier, as the imported from Chinese suppliers, to verify if the results
are acceptable as the prototype amplifier, this change is thinking on low the cost,
but thinking on quality maintenance.
With this change other could be performed, as change all the through-hole components
by the surface mount (SMD). This should low the costs and could lower the board dimensions.
Other change that could be performed is change the trimmers potentiometers by programmable
resistors, this change will be responsible by adjust the amplifier gain automatically.
It is ideal to perform the magnet wrapping automatically. This improvement will help on time
production, component quality, component cost and component dimensions.
Other improvement is to comunicate with the firmware using wirless communication,
this advance will bring more mobility to the gadget, because the firmware will not more be
assembled on the PCB, which signifies that it will not have the PC connection cable from the guitar.
